cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_quadratic

>>>>

The `gen_quadratic(n, p, range)` function generates a dataset of $n$ points forming a quadratic curve in the first two dimensions of a $p$-dimensional space. This $2\text{-}D$ parabolic structure is embedded within a higher-dimensional space with additive noise in the remaining dimensions.

The curve is constructed by drawing uniformly spaced inputs and applying a second-degree polynomial transformation. Let $X\_1 \sim \mathcal{U}(\text{range}\[1], \text{range}\[2])$ be the independent variable. A raw polynomial basis of degree 2 is used to form $X\_2 = X\_1 - X\_1^2 + \varepsilon\_2$, where $\varepsilon\_2 \sim \mathcal{U}(0, 0.5)$.

This creates a smooth parabolic arc that opens downward, with jitter in the vertical direction to simulate measurement noise or intrinsic variability.

For $p > 2$, the dataset includes Gaussian noise in the remaining dimensions via `gen_noisedims()`:

$$
X\_j \sim \mathcal{N}(0, 0.1^2), \quad j = 3, \dots, p.
$$
